\documentclass[]{article}

%opening
\title{HED 110}
\date {February 1, 2016}
\author{}

\begin{document}

\maketitle

\tableofcontents

\pagebreak

\section{Study Guide}

\subsection{Chapter 1}
\begin{itemize}
	\item Introduction to Health
\end{itemize}

\subsection{Chapter 2}
\begin{itemize}
	\item Maintain Wellness
\end{itemize}

\subsection{Chapter 3}
\begin{itemize}
	\item Managing Stress
\end{itemize}

\subsection{Chapter 4}
\begin{itemize}
	\item Mental health
\end{itemize}

\section{The Why of Living}
\begin{itemize}
	\item The power of why
	\item Identify your dreams and goals 
	\item Design your life 
	\item Create Timeline 
	\item Identify Obstacles 
\end{itemize}

\section{Terms to Review}
\begin{itemize}
	\item Locus of Control
	\item Self Eficacy
	\item Time Management
\end{itemize}

\section{4th Class}
\subsection{Open book exam; Chapters 1-4 }
\begin{itemize}
	\item Internal Locus of Control - Taking the blame or responsibility for our own actions.
	\item External Locus of Control - Becoming the victim or Projecting responsibility.
\end{itemize}

\section{Seven Dimentions of Wellness}
\subsection{Physical}
\begin{itemize}
	\item Exercise 
	\item Diet
	\item Avoid harmful habits
	\item Making responsible decitions about sex
	\item Getting Medical and Dental Check ups
	\begin{itemize}
		\item Pro-Active
		\item Re-Active
	\end{itemize}
\end{itemize}

\subsection{Emotional}
\begin{itemize}
	\item Trust
	\item Self Esteem
	\item Self Acceptance 
	\item Self Confidence 
	\item Good Relatioinships 
	\item Negative Words
	\begin{itemize}
		\item IF
		\item TRY 
		\item MIGHT
		\item MAYBE
	
	\end{itemize}
\end{itemize}

\subsection{Intellectual}
\begin{itemize}
	\item Openness to new ideas.
	\item Motivatoin to master skills.
	\item To question and think critically.
	\item A sence of humor. 
\end{itemize}

\subsection{Spiritual...}
\begin{itemize}
	\item A set of guiding beliefs, pricipals, or values that give meaning or purpose in life.
\end{itemize}

\subsection{Interpersonal and Social}
\begin{itemize}
	\item Satisfying Physical and emotional relationships.
	\item Supportive people around us. 
\end{itemize}

\subsection{Enviromental or Planetary}
\begin{itemize}
	\item Safety of the food supply.
	\item Air Pollution.
	\item Water pollution.
	\item Mold in the home.
	\item Second hand tobacco smoke.
\end{itemize}

\subsection{Financial}
\begin{itemize}
	\item Passive Income
	\item Active Income
\end{itemize}

\subsection{Chronic Disease}
\begin{itemize}
	\item Cause by personal choices or lifestyle.
	\begin{itemize}
		\item Prevention is the best treatment.
	\end{itemize}
	\item These are illnesses that are ongoing and reccurring that is not cause by infection or passed on by contact. 
	\begin{itemize}
		\item We make choices to increase or decrease illness. 
	\end{itemize}
\end{itemize}

\subsection{Self Eficacy}
\begin{itemize}
	\item An individuals belief in his or her capacity to execute behaviors necessary to produce specific perfomance attainment. It refects confidence in the ability to believe that "I can." 
	\item Belief/Faith
	\begin{itemize}
		\item The art of listening 
		\item Learn to agree to disagree.
		\item Retreat and regroup = Readjustment
	\end{itemize}
\end{itemize}

\subsection{Stages of change}

	\begin{itemize}
		\item Precontemplation = Denial 
		\item Contemplation = Maybe 
		\item Preparation = Getting help/ Decition to change. 
		\item Action = Moving towards change 
		\item Mainteinance = Steadyness 
		\item Termination = A part of Him/Her 
	\end{itemize}
	
	\begin{itemize}
		\item Become Familiar with:
		\begin{itemize}
			\item healthy people in 2020
			\item Diabetes
			\item Immune system
			\item Mind and body healing 
			\item Visualization
		\end{itemize}
		
	\end{itemize}
	
\section{Questions/Comments}

\begin{itemize}
		\item What is the difference between infectious and chronic disease?
		\item What causes infectious disease?
\end{itemize}


\end{document}
